Are populations like a circuit? The relationship between isolation by distance and isolation by resistance

### 2018-10-23 isolation_by_coalescence.tex
minor fixen

Thanks to David Levin for useful suggestions regarding hitting time calculations,
to Paul Marjoram for useful comments,
to Brad Shaffer and Evan McCartney-Melstad for discussions about landscape modeling,
and to John Novembre, Hussein Al-Asadi and Benjamin Peter for help with EEMS
and general input.
We would also like to gratefully acknowledge the immense positive impact that Brad McRae \citep[1966--2017;][]{lawler2018tribute}
has had on landscape genetics and conservation biology through the introduction of landscape resistance.
We hope this paper helps to carry forward this work.

@@

\begin{figure}
\centering
    \includegraphics{figs/all_flat_divergences}
\caption{
    Comparison of mean coalescence times between samples and between replicates
    for a $4 \times 4$ discretization of a square landscape with uniform migration.
    Between the 16 geographic regions, there are 136 comparisons;
    these are shown for two nonverlapping samples taken from three independent replicate simulations,
    each plotted against the the mean value across all replicates.
    Colors denote simulation replicate,
    and point type (circle/triangle) denotes the sample.
    Without sampling or process noise, all points would fall on the $y=x$ line.
    Among the six sets of observations,
    simulation replicate explains 6.7\% of the variance,
    and spatial sampling explains 13.8\% of the variance.
    } \label{fig:h_val_comp}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/barrier_locations}
    \includegraphics[width=0.45\textwidth]{figs/barrier_eems}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_dists}
    \caption{
        Results from the \textbf{barrier} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the the resistance distance method.
        \label{sfig:barrier_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/valley_locations}
    \includegraphics[width=0.45\textwidth]{figs/valley_eems}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_dists}
    \caption{
        Results from the \textbf{valley} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the the resistance distance method.
        \label{sfig:valley_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/expansion_locations}
    \includegraphics[width=0.45\textwidth]{figs/expansion_eems}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_dists}
    \caption{
        Results from the \textbf{expansion} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the the resistance distance method.
        \label{sfig:expansion_results}
    }
\end{figure}

>>>>

Thanks to David Levin for useful suggestions regarding hitting time calculations,
to Paul Marjoram for useful comments,
to Brad Shaffer and Evan McCartney-Melstad for discussions about landscape modeling,
and to John Novembre, Hussein Al-Asadi and Benjamin Peter for help with EEMS
and general input.
We would also like to gratefully acknowledge the immense positive impact that Brad McRae \citep[1966--2017;][]{lawler2018tribute}
has had on landscape genetics and conservation biology through the introduction of landscape resistance.
We hope this paper helps to carry forward this work.
Work on this project was supported by funding from
the Sloan Foundation and the NSF (under DBI-1262645) to PR.

@@

\begin{figure}
\centering
    \includegraphics{figs/all_flat_divergences}
\caption{
    Comparison of mean coalescence times between samples and between replicates
    for a $4 \times 4$ discretization of a square landscape with uniform migration.
    Between the 16 geographic regions, there are 136 comparisons;
    these are shown for two nonoverlapping samples taken from three independent replicate simulations,
    each plotted against the mean value across all replicates.
    Colors denote simulation replicate,
    and point type (circle/triangle) denotes the sample.
    Without sampling or process noise, all points would fall on the $y=x$ line.
    Among the six sets of observations,
    simulation replicate explains 6.7\% of the variance,
    and spatial sampling explains 13.8\% of the variance.
    } \label{fig:h_val_comp}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/barrier_locations}
    \includegraphics[width=0.45\textwidth]{figs/barrier_eems}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_dists}
    \caption{
        Results from the \textbf{barrier} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the resistance distance method.
        \label{sfig:barrier_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/valley_locations}
    \includegraphics[width=0.45\textwidth]{figs/valley_eems}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_dists}
    \caption{
        Results from the \textbf{valley} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the resistance distance method.
        \label{sfig:valley_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/expansion_locations}
    \includegraphics[width=0.45\textwidth]{figs/expansion_eems}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_dists}
    \caption{
        Results from the \textbf{expansion} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the resistance distance method.
        \label{sfig:expansion_results}
    }
\end{figure}
